A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-04-14 paper.tex

\begin{theorem}[See also \cite{SWchar}] \label{4d_minimal_twist_thm}
The holomorphic twist of 4d $\cN=1$ super Yang--Mills with matter valued in a $\fg$-representation-representation $R$ is perturbatively equivalent to holomorphic BF theory with the space of fields $T^*[-1]\map(\CC^2, R/\fg)$. 
Moreover, the equivalence is $\U(2)$-equivariant.
\end{theorem}

>>>>

\begin{theorem}[See also \cite{SWchar}] \label{4d_minimal_twist_thm}
The holomorphic twist of 4d $\cN=1$ super Yang--Mills with matter valued in a $\fg$-representation $R$ is perturbatively equivalent to holomorphic BF theory with the space of fields $T^*[-1]\map(\CC^2, R/\fg)$. 
Moreover, the equivalence is $\U(2)$-equivariant.
\end{theorem}
